Fast Dictionary Learning for High-Dimensional Seismic Reconstruction

### 2020-11-09 sgk5d/paper.tex
sgk

\plot{synth-ss}{width=\columnwidth}{width=0.3\columnwidth}{Single-trace comparison. The black line corresponds to the ground-truth solution. The green line corresponds to the noisy data. The pink line corresponds to the proposed method, which is closest to the black line. The red line corresponds to the KSVD method. The blue line corresponds to the DDTF method.}

@@

\multiplot{4}{hyper-mssa,hyper-ksvd,hyper-ddtf,hyper-sgk}{width=0.30\columnwidth}{Reconstructed data using (a) Rank-reduction method (SNR=9.68 dB), (b) KSVD (SNR=10.84 dB), (c) DDTF (SNR=11.45 dB), and (d) SGK (SNR=11.00 dB). All DL based methods use the result from the rank-reduction method as the initial model.}

@@

\inputdir{field}
\multiplot{4}{f-obs,f-ksvd,f-ddtf,f-sgk}}{width=0.30\columnwidth}{\new{3D Field data example. (a) Observed data. Reconstructed data using (b) KSVD, (c) DDTF, and (d) SGK.}}
\multiplot{4}{f-s-obs0,f-s-ksvd0,f-s-ddtf0,f-s-sgk0}{width=0.30\columnwidth}{2D slice comparison of the field data example. (a) Observed data. (b) Reconstructed data using KSVD. (c) Reconstructed data using DDTF. (d) Reconstructed data using SGK. The frame boxes are zoomed and shown in Figure \ref{fig:fz-obs,fz-ksvd,fz-ddtf,fz-sgk}.}

\multiplot{4}{fz-obs,fz-ksvd,fz-ddtf,fz-sgk}{width=0.30\columnwidth}{Zoomed 2D slice comparison of the field data example. (a) Observed data. (b) Reconstructed data using KSVD. (c) Reconstructed data using DDTF. (d) Reconstructed data using SGK. }

>>>>

\plot{synth-ss}{width=\columnwidth}{Single-trace comparison. The black line corresponds to the ground-truth solution. The green line corresponds to the noisy data. The pink line corresponds to the proposed method, which is closest to the black line. The red line corresponds to the KSVD method. The blue line corresponds to the DDTF method.}

@@

\multiplot{4}{hyper-mssa,hyper-ksvd,hyper-ddtf,hyper-sgk}{width=0.40\columnwidth}{Reconstructed data using (a) Rank-reduction method (SNR=9.68 dB), (b) KSVD (SNR=10.84 dB), (c) DDTF (SNR=11.45 dB), and (d) SGK (SNR=11.00 dB). All DL based methods use the result from the rank-reduction method as the initial model.}

@@

\inputdir{field}
\multiplot{4}{f-obs,f-ksvd,f-ddtf,f-sgk}{width=0.40\columnwidth}{\new{3D Field data example. (a) Observed data. Reconstructed data using (b) KSVD, (c) DDTF, and (d) SGK.}}
\multiplot{4}{f-s-obs0,f-s-ksvd0,f-s-ddtf0,f-s-sgk0}{width=0.40\columnwidth}{2D slice comparison of the field data example. (a) Observed data. (b) Reconstructed data using KSVD. (c) Reconstructed data using DDTF. (d) Reconstructed data using SGK. The frame boxes are zoomed and shown in Figure \ref{fig:fz-obs,fz-ksvd,fz-ddtf,fz-sgk}.}

\multiplot{4}{fz-obs,fz-ksvd,fz-ddtf,fz-sgk}{width=0.40\columnwidth}{Zoomed 2D slice comparison of the field data example. (a) Observed data. (b) Reconstructed data using KSVD. (c) Reconstructed data using DDTF. (d) Reconstructed data using SGK. }
